\documentclass{resume}

\usepackage[left=0.6in,top=0.5in,right=0.6in,bottom=0.6in]{geometry}
\usepackage{verbatim}

\name{Cyrus Vafadari}
\address{\textsc{2153 Massachusetts Ave \\ Cambridge MA 02140}}
\address{706~$\cdot$~587~$\cdot$~3715 \\ \textsc{cyrusv@alum.mit.edu}}

\begin{document}

%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf MIT} \hfill {\em 2012} \\ 
B.S. Nuclear Science and Engineering, 4.6/5.0

\end{rSection}

%------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Sookbox, LLC}{2011 - 2014}{CTO}{Cambridge, MA}
\item Raised \$1.2M to develop a home media streaming and playback solution
\item Designed and wrote back-end in primarily Python (rewritten from PHP)
\item Designed platform for multi-node architectures, remote message calling, and data marshalling
\item Managed team of 5 engineers
\end{rSubsection}

\begin{rSubsection}{Monte Carlo Methods for Parallel Processing of Diffusion Equations}{2012 - 2013}{Thesis}{Cambridge, MA}
\item Modelled neutron flux in reactors as systems of differential equations approximated by linear systems
\item Used a message passing interface in C to parallelize a Monte Carlo method to calculate solution vectors
\item Dynamically determined the number of random walks necessary to decrease runtime while ensuring a given confidence
\end{rSubsection}


\begin{rSubsection}{Compact Muon Solenoid, LHC, CERN}{2010}{Research Scientist}{Geneva, Switzerland}
\item Observation of Long-Range, Near-Side Angular Correlations in Proton-Proton Collisions at the LHC
\item Predicting probability of piled-up vertices as a function of multiplicity in proton-proton collisions
\item Analyzed over a billion collisions and Monte Carlo simulations in a C++ framework
\item Used Condor for grid computing
\item Discovered evidence of quark-gluon plasma in high-multiplicity p-p collisions, never before observed
\item Project publication: doi:10.1007/JHEP09(2010)091s
\end{rSubsection}


\begin{rSubsection}{Dept. Molecular Biology, Mass. General Hospital}{2009-2013}{Research Scientist}{Boston, MA}
\item Third author: "Radiation Resistance of Biological Reagents for In Situ Life Detection"
\item SETG, MIT/Harvard group designing and constructing a life-detection device to work on Mars
\item Designed and executed experiments simulating cosmic radiation on a flight to Mars
\item Irradiated over \$40,000 of reagents with over 10 Gy of radiation from 5 different types of radiation
\item Project publication: 10.1089/ast.2012.0869
\end{rSubsection}


%------------------------------------------------

\end{rSection}

\begin{rSection}{Patents}
\begin{rSubsection}{Pending}{Filed January 2014}{Co-Inventor}{}
\item Method and System for Providing Digital Content. US PCT/US2014/010243.
\item Digital Content Connectivity and Control via a Plurality of Controllers that are treated as a Single Controller. US 14/147,397.
\item Digital Content Connectivity and Control via a Plurality of Controllers that are Treated Discriminatively. US 14/149,541.
\item Configuring, Networking, and Controlling a Plurality of Unique Network-Capable Devices. US 14/149,726.
\end{rSubsection}

\end{rSection}


\begin{comment}

\begin{rSection}{Activities}
\begin{rSubsection}{Track and Field}{2005-2013}{Pole Vault}{}
\item MIT Varsity, PR 4.85m (16 ft)
\item All-New England (DI, DII, and DIII)
\item 2-time New England DIII Champion
\end{rSubsection}

\begin{rSubsection}{Sigma Alpha Epsilon}{2009-2013}{Founding member, 1st President}{}
\item Nation-­wide Colony of the Year, 2-­time winner of MIT Service Cup, nation-wide Zeal Award winner, MIT Best New Member Program, and MIT Most Improved Chapter
\item Served as recruitment chair (60\% increase in membership in my officership), managed \$10,000 budget

\end{rSubsection}

\end{rSection}
\end{comment}

\end{document}